\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-13 manuscript/manuscript.tex
parametric bootstrap need to test

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution. The null hypothesis $H_0$ is that $X_i$'s follow the
hypothesized distribution~$F$.
Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function. The KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}

The statistic 
can be used to see if a population follows a hypothesized distribution and has 
and can be applied to a variety of fields. It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}. \citet{zeimbekakis2022misuses} reviews
some of the common misuses of the one-sample KS test. One of the most common 
misuses of the KS test is when
the hypothesized distribution has unspecified parameters. 
\citet{babu2004goodness} approaches this scenario using basic 
non-parametric bootstrap. There is also the scenario where the data are serially
dependent, which \citet{zeimbekakis2022misuses} partially remedies with 
semi-parametric
bootstrap. The last scenario \citet{zeimbekakis2022misuses} discusses is that
where both the hypothesized 
distribution has unspecified parameters and the data are 
serially dependent. \citet{zeimbekakis2022misuses}'s remedy for
this scenario also uses semi-parametric bootstrap.

A complete remedy for KS tests with serially dependent data is
a challenging task. The null distribution depends on the structure of the serial
dependence, which can be arbitrary in practice. A parametric bootstrap procedure
would demand a specification for a model for the dependence, whereas the primary 
interest
is to test the marginal distribution of the stationary series. A bias 
correction
for block bootstrap similar to what \citet{babu2004goodness} did for basic
bootstrap had not yet been shown.  This study aims to resolve this gap by 
demonstrating a bias 
correction
for non-parametric block bootstrap to use when the hypothesized distribution
has unspecified parameters and the data are serially dependent.

>>>>

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. 
Let $X_1, ..., X_n$ be a random sample of size~$n$ from some continuous
distribution and the null hypothesis $H_0$ be that $X_i$'s follow the
hypothesized distribution~$F$.
If we let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function, the KS test statistic takes the form
\begin{equation}
  \label{eq:ks_standard}
  T_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}

The KS statistic 
can be used to see if a population follows a hypothesized distribution and has 
and can be applied to a variety of fields. It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}. \citet{zeimbekakis2022misuses} reviews
some of the common misuses of the one-sample KS test. One of the most common 
misuses of the KS test is when
the hypothesized distribution has unspecified parameters. 
\citet{babu2004goodness} approaches this scenario using basic 
non-parametric bootstrap. There is also the scenario where the data are serially
dependent, which \citet{zeimbekakis2022misuses} partially remedies with 
semi-parametric
bootstrap. The last scenario \citet{zeimbekakis2022misuses} discusses is that
where both the hypothesized 
distribution has unspecified parameters and the data are 
serially dependent. \citet{zeimbekakis2022misuses}'s remedy for
this scenario also uses semi-parametric bootstrap.

A non-parametric remedy for KS tests with serially dependent data is
a challenging task. The null distribution depends on the structure of the serial
dependence, which can be arbitrary in practice. A parametric bootstrap procedure
would demand a specification for a model for the dependence, whereas the primary 
interest
is to test the marginal distribution of the stationary series. A bias 
correction
for block bootstrap similar to what \citet{babu2004goodness} did for basic
bootstrap had not yet been shown.  This study aims to resolve this gap by 
demonstrating a bias 
correction
for non-parametric block bootstrap to use when the hypothesized distribution
has unspecified parameters and the data are serially dependent.
